---
title: "2/6 Notes"
author: "Gavin Nelson"
format: html
editor: visual
---

## 2/6 Notes

```{r}
if(!require("pacman")) install.packages("pacman")
pacman::p_load_gh("ccolonescu/POESRdata")
pacman::p_load_gh("ccolonescu/PoEdata")

load(andy)
head(andy)
```



```{r}
pacman::p_load("jtools")

andy.sales <- lm(sales ~ price + advert, data = andy)
sum(andy.sales)

```

diminishing returns here but model does not show this, means relationship is non-linear


```{r}
psych::pairs.panels(andy)
```

We can see the diminishing returns in sales/advert scatterplot


```{r}
plot.fitted(andy.sales)
```

Want to see most points in the dark gray, less in light gray, none(?) in white space



quadratic model
```{r}
mod2 <- lm(sales ~ price + I(advert^2), data = andy)
#I treats inside as math
summary(mod2)
plot.fitted(mod2)
```

concave up/down will be created by quadratic, will show a point of diminishing returns
R-squared went up as we added another parameter


```{r}
#space
```

### Doing a log-log model

```{r}
mod3 <- lm(log(sales) ~ log(price), data = andy)
```

think sign will change - quadratic
not - log

elasticity - percent change x / percent change y
  - how much will y change if x chnages by a certain percent

```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```

