---
title: "2/6 Notes"
author: "Gavin Nelson"
format: html
editor: visual
---

## 2/6 Notes








```{r}
if(!require("pacman")) install.packages("pacman")
pacman::p_load_gh("ccolonescu/POESRdata")
pacman::p_load_gh("ccolonescu/PoEdata")

load(andy)
head(andy)
```



```{r}
pacman::p_load("jtools")

andy.sales <- lm(sales ~ price + advert, data = andy)
sum(andy.sales)

```

diminishing returns here but model does not show this, means relationship is non-linear


```{r}
psych::pairs.panels(andy)
```

We can see the diminishing returns in sales/advert scatterplot


```{r}
plot.fitted(andy.sales)
```

Want to see most points in the dark gray, less in light gray, none(?) in white space



quadratic model
```{r}
mod2 <- lm(sales ~ price + I(advert^2), data = andy)
#I treats inside as math
summary(mod2)
plot.fitted(mod2)
```

concave up/down will be created by quadratic, will show a point of diminishing returns
R-squared went up as we added another parameter


```{r}
#space
```

### Doing a log-log model

```{r}
mod3 <- lm(log(sales) ~ log(price), data = andy)
```

think sign will change - quadratic
not - log

elasticity - percent change x / percent change y
  - how much will y change if x changes by a certain percent
  
  
  
  
  KNOW THE BACKGROUND OF THE DATA


# 2/8 Notes

slope is variables against each other
elasticity - number stays constant, percent change in x over percent change in y

log-liner vs. linear-log


use logs b/c they take non-linear graphs and change them into linear-like graphs

in general,d ont vare about llog of y, just y, problem with then doing exp(y), is that there will be some bias
  - to fix it, multiply by e to sigma squared over 2, standard error of y hat


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```

